\section{Criteria} \label{sc:criteria}
In this section the criteria for the system have been prioritized based on the criterion analysis model described in \cite[chap 9]{OOAD}.

\begin{table}[H]
    \centering
    \resizebox{\textwidth}{!}{%
    \begin{tabular}{|l|c|c|c|c|}
        \hline
        \textbf{Criterion} & \textbf{Very important} & \textbf{Important} & \textbf{Less important} & \textbf{Irrelevant} \\
        \hline
        \hline
        Usable & $\pmb{\times}$ & & & \\
        \hline
        Secure & & & $\pmb{\times}$ & \\
        \hline
        Efficient & & & $\pmb{\times}$ & \\
        \hline
        Correct & $\pmb{\times}$ & & & \\
        \hline
        Reliable & & $\pmb{\times}$ & & \\
        \hline
        Maintainable & & $\pmb{\times}$ & & \\
        \hline
        Testable & & $\pmb{\times}$ & & \\
        \hline
        Flexible & $\pmb{\times}$ & & & \\
        \hline
        Comprehensible & & $\pmb{\times}$ & & \\ 
        \hline
        Reuseable & & & & $\pmb{\times}$ \\
        \hline
        Portable & & & & $\pmb{\times}$ \\
        \hline
        Interoperable & & & & $\pmb{\times}$ \\
        \hline
    \end{tabular}
    }
    \caption{Checklist for prioritizing design criteria}
    \label{tab:my_label}
\end{table}

\textbf{Usable:} One of the primary reasons for Aalborg Zoo to get a system developed from scratch was to get a system that is easy and intuitive to navigate. Therefore, this is a very important element of the system and the final product. The system is primarily built with usability in focus.

\textbf{Secure:} As the product does not contain any confidential information, security in the system is considered less important. However there is still a minor focus on security, as access to the functions within the program is limited to users with the required permissions and only users who have already been added to the database can access anything in the system.

\textbf{Efficient:} The client has expressed that the efficiency of the system is of little concern, so this criteria is considered less relevant. However, it should still be able to complete the tasks within a reasonable amount of time.

\textbf{Correct:} Aalborg Zoo has given weighted requirements for the system, as seen in \autoref{sc:requirements}. It is very important that the requirements are met upon delivering the finished product, so correctness is marked as very important.

\textbf{Reliable:} As part of the heavy focus on the user experience, it is important that the system behaves in a predictable manner, and does this reliably.

\textbf{Maintainable:} The client has expressed a desire for the program to be maintainable, as they want to maintain the system themselves. Because they are not experts in programming, the system should be as easily maintainable as possible and built on industry standards. The code base should also avoid high reliance on smaller packages, which might lose support in the future.

\textbf{Testable:} As with all other systems, this system should be developed in such a way, that it is testable. One of the most reliable ways of ensuring that the other criteria are fulfilled is by testing the system, but is not as important to the client as some of the other criteria. Therefore, making a testable system has been marked as important.

\textbf{Flexible:} The client wants to be able to further develop the system after the product is delivered. Therefore it is very important that it is flexible and without too many dependencies. One of the changes that are likely to happen in the future is change of database type.

\textbf{Comprehensible:} The system should be comprehensible, as the client have mentioned that they might make adjustments to the system at a later time. This requires the system to be design in such a way that different components and their connections can easily be understood. This is marked as important instead of very important, as the client would prefer a less comprehensible system with lots of functionality, compared to a comprehensible one with less functionality.
% The system should be comprehensible, as the less experienced users should be able to carry out simple tasks in the system easily. High comprehension also allows the client to easily add the functionality they need later on. For this reason, this criterion is important.

\textbf{Reusable:} No part of the system will be used in other systems and therefore, this criterion is irrelevant.

\textbf{Portable:} The system will only be built for a Windows PC, and for this reason, there is no need for the system to be portable. 

\textbf{Interoperable:} The system will not communicate with other systems, beside the database component, which means this criterion is irrelevant for the system.