\subsection{PACT analysis}\label{ssc:PACT}
A PACT analysis \cite[chap 2]{DEB} has been performed to better understand the interactions between the users and the system. The analysis gives a better description of the users, their needs and restrictions, the context in which the system is used, the activities surrounding the system, and the technologies involved.\\

\textbf{People}:\\
%(Physiological differences, Psychological differences, Social differences, Domain Expertise)
It is important to analyse the interactions with the system, to ensure ease of use for the people using the system. It should be taken into consideration, how these people are different from each other and what special needs they might have. First we list the people who will interact with the system:

\begin{itemize}
    \setlength\itemsep{0.05em}
    \item Admins at the zoo (primarily at the IT department)
    \item Employees at the zoo
\end{itemize}

The presented people have no psychological, physiological, or social differences to speak of. The respondents from the zoo, Morten and Kasper, both work in the IT department, which means they are used to working with computers. They are the main focus of the system, as they are the ones who will use it the most. However, they have requested the interface to be minimalistic and easy to use. The other employees at the zoo are expected to have experience with computer-based systems through their work, but not as deep of an understanding as Morten and Kasper. This information has been derived from the interviews with Morten and Kasper.\\

\textbf{Activities}: \\
%(Purpose of activities to be supported by the system, Temporal aspects, Collaboration, Complexity, Safety criticality, Nature of system content) \\
The users of the system will be using the system to keep track of assets and export lists of assets. They will keep track of the assets by adding them to, editing them in, and removing them from the system. They will also print out a list of changes made to the assets. On occasion they may also want a specific asset and will search through the database. Some users will only use the system to see assets and their state, and comment on them. The system will also be used to create groups of assets based on tags.\\

\textbf{Context}: \\
%(Physical, Social, Organizational) \\
The system will be used at Aalborg Zoo, primarily on desktops and laptops located within the zoo. The laptops might be moved around the premise. The social context at the zoo is not expected to be affected by the system, as it does not contain any elements geared towards any social aspects.\\
 
\textbf{Technology}:
%(That could support users in the domain)
The relevant technologies related to the system and its implementation include the following:

\begin{itemize}
    \setlength\itemsep{0.05em}
    \item Computer
    \item Screen
    \item Barcode scanner
    \item Mouse
    \item Keyboard
    \item Database
    \item Internet
\end{itemize}

The computer will be used to run the system and the screen will be used as an output device, while the barcode scanner, mouse, and keyboard will be used for input. The database will function as storage for everything added to the system, such as assets and tags, and the internet will be used in the context of connecting to the database and maintaining the model on all connected devices running the system.
\par
With a deeper understanding of the people, activities, contexts, and technologies surrounding the system, it is easier to design the user interface of the system.