\section{Usage}\label{sc:usage}
Within this section, the usage of the system, which include a list of actors and relevant use cases, has been analysed. This part of the application domain is important to understand, to satisfactorily create the user experience and offer all the relevant functionality in the finished system. Firstly, the actors and use cases has been identified and connected in an actor table.
\par
The actors in the application domain only include the employees and admins. The differentiation of the two is made, because the admin has access to specific functionality and pages within the system, which are invisible for the employee. The admin class is a specialization of the employee class, which means it has the same abilities as the employee, but is granted further interactions with the system.
\par
Based on the system definition and requirements-list, the use cases have been constructed (see \autoref{tab:actor_table}). These are the relevant use cases to handle the assets.

\begin{table}[H]
    \centering
    % \hrule
    \vspace{0.2cm}
    \hspace{6cm} \vspace{0.6cm} \textbf{Actors}
    \begin{tabular}{p{0.5\textwidth} || p{0.2\textwidth} p{0.2\textwidth}}
        \textbf{Use cases} & Admin & Employee \vspace{0.2cm}\\
        \hline \hline
        Add an asset & \hspace{0.34cm} $\pmb{\times}$ & \\
        \hline
        Loan out an asset & \hspace{0.34cm} $\pmb{\times}$ & \hspace{0.6cm} $\pmb{\times}$ \\
        \hline
        Return an asset & \hspace{0.34cm} $\pmb{\times}$ & \hspace{0.6cm} $\pmb{\times}$ \\
        \hline
        Change the information about an asset & \hspace{0.34cm} $\pmb{\times}$ & \\
        \hline
        Remove an asset & \hspace{0.34cm} $\pmb{\times}$ & \\
        \hline
        Search for an asset & \hspace{0.34cm} $\pmb{\times}$ & \hspace{0.6cm} $\pmb{\times}$ \\
        \hline
        Print a report of assets & \hspace{0.34cm} $\pmb{\times}$ & \\
        \hline
        Comment an asset & \hspace{0.34cm} $\pmb{\times}$ & \\
    \end{tabular}
    \vspace{0.2cm}
    % \hrule
    \vspace{0.2cm}
    \caption{Actor table of the relations between actors and use cases.}
    \label{tab:actor_table}
\end{table}

In the actor table above (see \autoref{tab:actor_table}), it has become clear that the admin takes part in every use case. This can be explained by the way the system will be used. The system should function almost like an interface to a database, so it makes sense that the admin will be involved in all the changes made to the system and, as an effect of this, the database. The actors has been further described in the following section.