\section{Actors}\label{sc:actors}

The system will be used by two different types of actors, \textit{Admins} and \textit{Viewers}. These are described as followed:

\begin{actor}[H]
    \hrule
    \vskip 0.3cm
    \Large
    \begin{center}
        \textbf{Admin}
    \end{center}
    \vskip 0.1cm
    \hrule
    \vskip 0.2cm
    \normalsize
    
    \textbf{Goal:} The \textit{admin} manages the system. The \textit{admin's} basic need is to keep track of their assets.
    
    \vskip 0.2cm
    
    \textbf{Characteristics:} The \textit{admin} is the primary user of the system, and is the only actor who can change anything regarding the assets in the system. They are experienced with using enterprise systems and handling the assets of their department.
    
    \vskip 0.2cm
    
    \textbf{Examples:} \textit{Admin A} is used to organising large quantities of assets, and sees the asset management system as a supplement to their organisational tools.
    \vskip 0.1cm
    \textit{Admin B} is new to asset management, and needs a tool that can help them in all aspects of organising.
    
    \vskip 0.4cm
    \hrule
    \vskip 0.2cm
    \caption{Adding an asset} \label{actor:admin}
\end{actor}


\begin{actor}[H]
    \hrule
    \vskip 0.3cm
    \Large
    \begin{center}
        \textbf{Viewer}
    \end{center}
    \vskip 0.1cm
    \hrule
    \vskip 0.2cm
    \normalsize
    
    \textbf{Goal:} The \textit{viewer} can observe the system's content. Their need is to get an overview of the status of different assets that might be relevant for their work. 
    
    \vskip 0.2cm
    
    \textbf{Characteristics:} The \textit{viewer} is the secondary user of the system. They can only comment on assets in the system. They have varying degrees of technical competence.
    
    \vskip 0.2cm
    
    \textbf{Examples:} \textit{Viewer A} is familiar with computer systems and has no trouble finding their way around the asset management system.
    \vskip 0.1cm
    \textit{Viewer B} is less experienced with computer systems and is more comfortable talking directly to the admin instead of using the system themselves. 
    
    \vskip 0.4cm
    \hrule
    \vskip 0.2cm
    \caption{Adding an asset} \label{actor:viewer}
\end{actor}

