\chapter{Usability Test Tasks} \label{app:usabilityTest}

The introduction to both the admin and the employee usability tests are the same. They introduce the system and thanks the test participant for their help. The introductions for the admin test can be seen below followed by the list of tasks given during the admin tests and employee tests respectively. 

\section*{Admin introduction}

\begin{quote}
    \textit{Today you will interact with out Asset Management System. You will be asked to perform 10 tasks. During the test you will be asked to talk aloud about your thoughts, which expectations you have when interacting with the different parts of the system, and how you with to perform a task.
    \\
    After you have solved the tasks we will walk you through your experience and any problems you may have had. This follow-up will provide you with the opportunity to get answers to ask any questions you may have. 
    \\\\
    By participating in this test, you accept that we collect data for use in analysis of the system.
    \\\\
    Thank you for your participation. We appreciate your help.}
\end{quote}


\section*{Admin tasks}

\begin{enumerate}
    \item You have received a large shipment of switches and wish to add a common denominator for all switches that will be added in the future. You know that a switch always have an IP address. 
    \item You have received a new switch by the name "TL-10". The switch has been produced by "TP-Link". It has the IP address "149.220.101.90" and a unique bar code: 11S362-SKI19. Add the switch to the system with this information. 
    \item The number of ports on the switch needs to be added. this information should be connected to all switches in the system. There is often eight ports on a switch. 
    \item There are 10 ports in the previously added switch. Add this information to that switch. 
    \item Export the added switch and two other elements in the program. 
    \item The switch has now been discarded and should no longer be in the system. 
    \item You are told that you will no longer be handling switches. delete the common denominator. 
    \item A lot of changes have been made to the system and you wish to get a list of the five latest changes. 
    \item New employees have been hired and should be added to the system. There is a file in the destination "Desktop -> Usability test -> Users".
    \item An employee had left a message on a computer regarding a problem with connecting to the internet. Go to that computer's page. 
\end{enumerate}


\section*{Employee tasks}

\begin{enumerate}
    \item You have borrowed a computer from the IT department but they forgot to give you the password. Find it in the system. The borrowed computer is a  Lenovo Yoga C930 with the ID "LOIKJHGF".
    \item The password is obsolete so you want to leave a message for the administrator to let them know. 
\end{enumerate}


\section*{Final questions}
After the test participant had finished doing the given tasks, the following questions were asked:

\begin{itemize}
    \item Did you feel like the interface supported the way you wanted to solve the tasks? Why/Why not?
    \item Were there any functionalities you were not offered, that could have improved the experience and made the tasks easier? Which?
    \item Did you feel that the different buttons and functions acted like you expected? Why/Why not?
    \item Did you feel like the design was confusing or distracting? Why/Why not?
\end{itemize}