\chapter{Discussion}\label{ch:discussion}

\section{Fulfillment of requirements}
% Requirements der ikke er opfyldt

Not all the requirements for the system were implemented. 
\\
The ones that were not implemented are:
\par
When searching for assets, a list of tags on the found assets will be shown. From this list it will be possible to hide assets by deselecting tags. 
\par
Assets can expire, and the system should inform the user of this.
\par
Notifications will be based on function tags.
\par
Viewers can request an asset. The admins can view, approve, or deny all requests for assets.
\par
% Wont have
AND, OR, and parentheses can be used to enable complex searching. % Kunne argumenterer at der kan gøres noget lignende ved at søge på tags
\par
System functions can be linked to barcodes.

\par
The requirements in \textit{Wont have this time} were not expected to be fulfilled in this project. 

\section{Fulfillment of criteria}
% Lever vi op til very important & important?
In criteria for the system described in \autoref{sc:criteria}, there are three criteria that are categorized as very important. These are Usable, Correct, and Flexible.
% Usable kan bekræftes opfyldt gennem usability tests?
% Correct kan bekræftes gennem usability tests og om det lever op til requirements.
% Flexible? 
\par
There are also three important criteria. These are Reliable, Maintainable, and Comprehensible.
% Reliable burde kunne bekræftes gennem tests.
% Maintainable
% Comprehensible

\section{Design pattern}
% mvvm og WPF m.m.
% Var det en god ide at bruge controllers?
    % Argumentet for at bruge dem var separation of concerns og et ønske om at holde modeller "pure"


\section{Tests}
% var de gode nok?
% Var de til nogen hjælp?
% usability tests
% Unit tests & integrations tests
    % Er det dækkende?
    
\section{Work method}
% iterativ metode
% refaktorering af program
    % Hvorfor var det vigtigt/ nødvendigt?
    % opnåede vi alt det vi ville med det?
% generel arbejdsmetode (fx møder, arbejdsfordeling mm)

\section{Fulfillment of curriculum}

