\chapter{Introduction}\label{ch:introduction}
As companies expand and acquire a growing number of assets, the desire to keep track of these assets and their condition can also grow \citep{ImportanceOfAM}. Creating an overview of the assets, and keeping this overview up to date, is a major task and one that companies sometimes do not address until the number of assets in their possession has become overwhelming \citep{DoNotIgnoreSAM}. These issues are clear when looking at the growing market of asset management software. The submarket of digital asset managements is estimated to grow from 1.2 billion in 2018, to 6,901 billion by 2024 \citep{MarketGrowth}.
\par
While there are many existing solutions, these are often very extensive and try to accommodate a lot of different use cases by adding more data points to the design \citep{SnipeIT}. This can however lead to the system becoming overwhelming itself. A way of making a solution more suitable for a wide range of companies while still keeping it simple, could be to make it more adaptable \citep{CustomSoftware}. With this approach, the individual company will not be overwhelmed with unneeded User Interface (UI) elements, that are only relevant for a few specific companies.
\par
Focusing on a specific department at a specific company, has limited the magnitude of the project. The collaborator of this project has been the IT department at Aalborg Zoo. Therefore, the specific needs of Aalborg Zoo has been a high priority, as they are considered the customer of the finished product.
\par
Aalborg Zoo is located in the center of Aalborg, and welcomes around 341.000 visitors each year \citep{AalborgZoo}. The zoo has 44 employees with different backgrounds and responsibilities \citep{AalborgZoo}. Because of this, the zoo is divided into multiple departments \citep{PersonaleAZ}. The IT department has multiple responsibilities, including supplying the other departments with computers, walkie talkies, routers, and more (see \autoref{sc:aalborgZoo}). In line with the growth of the zoo and technological advancements, the IT department has come in charge of a lot of different assets. These assets can be loaned out to any employee or department at any point, which can make it hard to keep track of their locations and conditions.
\par
To accommodate this growing task and to ensure an overview of the assets, the IT department has requested an asset management system.

\subsubsection*{Problem statement}
Based on the mentioned issues with existing solutions to the problem, the following problem statement has been formulated and used as the main focus of the project.

\begin{quote}
    \textit{How can a system be designed to be more adaptable than existing asset management systems?}
\end{quote}

% How can a system help Aalborg Zoo manage their assets better than existing tools can?

% How can a system be created to help the IT department at Aalborg Zoo manage their assets?

% How to develop a software system to help the IT department at Aalborg Zoo to manage their systems?

% How can a system, that helps Aalborg Zoo manage their assets, be designed and implemented?

% How can a software solution help manage Aalborg Zoo's assets?

