\section{Requirements}\label{sc:requirements}
Based on the interviews with the zoo and on the analyses above, a list of requirements have been formulated. According to the MoSCoW method these requirements have been divided into categories based on their priority. The final requirement specification can be seen in the following table (table \ref{tab:moscow}). This prioritisation has been approved by the it department at Aalborg zoo and will dictate the development of the system. 

\begin{longtable}{p{3.2cm} p{10cm}}
    \renewcommand{\arraystretch}{2.0}
        \\
        \hline
        \textbf{Must have} & 
        \vspace*{-7mm}
        \begin{enumerate} \itemsep0em 
            \item Assets can be added, removed, and edited
            \item It will be possible to search through all assets with either ID or name.
            \item Information on users will be imported from the Active Directory.
        \end{enumerate}
        \\
        \hline
        
        \textbf{Should have} & 
        \vspace*{-7mm}
        \begin{enumerate} \setcounter{enumi}{3} \itemsep0em 
            \item Assets and log entries can be exported to a file based on a search.
            \item Admins and viewers can add comments to assets. Admins can remove and edit all comments, while viewers can only edit their own comments.
            \item Comments for each asset will be accessible from within the specific asset.
            \item All changes to assets, tags, and comments will be logged.
            \item Fields will be set to a certain type and can be marked as required. It will be possible for a field to have a default value.
            \item The design will be very minimalist.
            \item Tags will be presented in different colors. Subtags will inherit the color of their parent tag. Colors will be assigned randomly if not chosen by the user.
        \end{enumerate}
        \\
        \hline
        
        \textbf{Nice to have} & 
        \vspace*{-7mm}
        \begin{enumerate} \setcounter{enumi}{10} \itemsep0em 
            \item Departments can be added, removed, and edited. Each user can set their default department.
            
            \item Tags are department specific.
            
            \item It will be possible to select multiple assets or select all and then deselect certain assets. The selected assets can then be exported to a file.
            
            \item When searching for assets, a list of tags on the found assets will be shown. From this list it will be possible to hide assets by deselecting tags.
            
            \item Assets can expire, and the system should inform the user the user of this.
            
            \item Notifications will be based on function tags.
            
            \item Viewers can request an asset. The admins can view, approve, or deny all requests for assets.
            
        \end{enumerate}
        \\
        \hline
        \textbf{Won't have} & 
        \vspace*{-7mm}
        \begin{enumerate} \setcounter{enumi}{17} \itemsep0em 
            \item AND, OR, and parentheses can be used to enable complex searching.
            \item System functions can be linked to barcodes.
        \end{enumerate}
        \\
        \hline
    \caption{MoSCoW}
    \label{tab:moscow}
   
\end{longtable}


%\textbf{Must have}: \label{Moscow}
%\begin{enumerate}
%    \item 
%    
%    \item Tags can be added to the assets. These tags may contain a number of fields. 
%    
%    \item It will be possible to search through all assets with either ID or name.
%    
%    \item Information on users will be imported from the Active Directory.
%\end{enumerate}

%\textbf{Should have}:
%\begin{enumerate}
%\setcounter{enumi}{4}
%    \item Assets and log entries can be exported to a file based on a search.
%    
%    \item Admins and viewers can add comments to assets. Admins can remove and edit all comments, while viewers can only edit their own %     comments.
%    
%    \item Comments for each asset will be accessible from within the specific asset.
%    
 %   \item All changes to assets, tags, and comments will be logged.
%    
%    \item Field will be set to a certain type and can be marked as required. It will be possible for a field to have a default value. 
%
%    \item The design will be very minimalist.
%    
%    \item Tags will be presented in different colors. Subtags will inherit the color of their parent tag. Colors will be assigned randomly if not chosen by the user. 
%\end{enumerate}

%\textbf{Nice to have}:
%\begin{enumerate}
%\setcounter{enumi}{11}
%    \item Departments can be added, removed, and edited. Each user can set their default department.
%    
%    \item Tags are department specific.
%    
%   \item It will be possible to select multiple assets or select all and then deselect certain assets. The selected assets can then be exported to a file. 
    
%    \item When searching for assets, a list of tags on the found assets will be shown. From this list it will be possible to hide assets by deselecting tags.    
    
%    \item Notifications will be based on function tags.\todo{Function tags skal forklares}
    
%    \item Viewers can request an asset. The admins can view, approve, or deny all requests for assets. 
%\end{enumerate}
    
%\textbf{Won't have}:
%\begin{enumerate}
%\setcounter{enumi}{17}
%    \item AND, OR, and parentheses can be used to enable complex searching.
    
%    \item System functions can be linked to barcodes. 
%\end{enumerate}
