\section{Method}
The project has been produced as a group project with a group of seven members. Throughout the project period, multiple courses have been attended by the members on a weekly basis, and these courses have been an academic basis for the entire project. The courses have taken time from the project work, but have contributed irreplaceable knowledge to the members of the group. The time not spent on courses has been used to develop this report and the product system.
\par
To ensure the quality of the end product, the development has been done using an iterative process, where the project as a whole has been entirely or partly redesigned through multiple iterations. The first iteration has consisted of disconnected parts, which were tested and evaluated. The later iterations have then been based on the tests and evaluations from the previous steps, and have conferred with a new basis based on the tests and evaluations of that iteration. Through this process, essential elements have been implemented early in the process for further testing opportunities and evaluation. This has also meant that the features less crucial to the system have been implemented later and as extra features rather than core functionalities.
\par
Though some features have been added at a later stage in the development cycle, all implemented features and core functionalities have been thoroughly tested and have succeeded these test. If a feature or functionality has failed the tests made for it, it has been removed from the final project and added to the list of additional features for the next version.